\section{List of Options}
\label{sec:charityList}
We provide the full list of options presented on the survey.

\begin{itemize}[leftmargin=*]
    \item \textbf{Animal Rights, Welfare, and Services:} Protect animals from cruelty, exploitation and other abuses, provide veterinary services and train guide dogs.
    \item \textbf{Wildlife Conservation:} Protect wildlife habitats, including fish, wildlife, and bird refuges and sanctuaries.
    \item \textbf{Zoos and Aquariums:} Support and invest in zoos, aquariums and zoological societies in communities throughout the country.
    \item \textbf{Libraries, Historical Societies and Landmark Preservation:} Support and invest public and specialized libraries, historical societies, historical preservation programs, and historical estates.
    \item \textbf{Museums:} Support and invest in maintaining collections and provide training to practitioners in traditional arts, science, technology, and natural history.
    \item \textbf{Performing Arts:} Support symphonies, orchestras, and other musical groups; ballets and operas; theater groups; arts festivals; and performance halls and cultural centers.
    \item \textbf{Public Broadcasting and Media:} Support public television and radio stations and networks, as well as providing other independent media and communications services to the public.
    \item \textbf{Community Foundations:} Promote giving by managing long-term donor-advised charitable funds for individual givers and distributing those funds to community-based charities over time.
    \item \textbf{Housing and Neighborhood Development:} Lead and finance development projects that invest in and improve communities by providing utility assistance, small business support programs, and other revitalization projects.
    \item \textbf{Jewish Federations:} Focus on a specific geographic region and primarily support Jewish-oriented programs, organizations and activities through grantmaking efforts
    \item \textbf{United Ways:} Identify and resolve community issues through partnerships with schools, government agencies, businesses, and others, with a focus on education, income and health.
    \item \textbf{Adult Education Programs and Services:} Provide opportunities for adults to expand their knowledge in a particular field or discipline, learn English as a second language, or complete their high school education.
    \item \textbf{Early Childhood Programs and Services:} Provide foundation-level learning and literacy for children prior to entering the formal school setting.
    \item \textbf{Education Policy and Reform:} Promote and provide research, policy, and reform of the management of educational institutions, educational systems, and education policy.
    \item \textbf{Scholarship and Financial Support:} Support and enable students to obtain the financial assistance they require to meet their educational and living expenses while in school.
    \item \textbf{Special Education:} Provide services, including placement, programming, instruction, and support for gifted children and youth or those with disabilities requiring modified curricula, teaching methods, or materials.
    \item \textbf{Youth Education Programs and Services:} Provide programming, classroom instruction, and support for school-aged students in various disciplines such as art education, STEM, outward bound learning experiences, and other programs that enhance formal education.
    \item \textbf{Botanical Gardens, Parks, and Nature Centers:} Promote preservation and appreciation of the environment, as well as leading anti-litter, tree planting and other environmental beautification campaigns.
    \item \textbf{Environmental Protection and Conservation:} Develop strategies to combat pollution, promote conservation and sustainable management of land, water, and energy resources, protect land, and improve the efficiency of energy and waste material usage.
    \item \textbf{Diseases, Disorders, and Disciplines:} Seek cures for diseases and disorders or promote specific medical disciplines by providing direct services, advocating for public support and understanding, and supporting targeted medical research.
    \item \textbf{Medical Research:} Devote and invest in efforts on researching causes and cures of disease and developing new treatments.
    \item \textbf{Patient and Family Support:} Support programs and services for family members and patients that are diagnosed with a serious illness, including wish granting programs, camping programs, housing or travel assistance.
    \item \textbf{Treatment and Prevention Services:} Provide direct medical services and educate the public on ways to prevent diseases and reduce health risks.
    \item \textbf{Advocacy and Education:} Support social justice through legal advocacy, social action, and supporting laws and measures that promote reform and protect civil rights, including election reform and tolerance among diverse groups.
    \item \textbf{Development and Relief Services:} Provide medical care and other human services as well as economic, educational, and agricultural development services to people around the world.
    \item \textbf{Humanitarian Relief Supplies:} Specialize in collecting donated medical, food, agriculture, and other supplies and distributing them overseas to those in need.
    \item \textbf{International Peace, Security, and Affairs:} Promote peace and security, cultural and student exchange programs, improve relations between particular countries, provide foreign policy research and advocacy, and United Nations-related organizations.
    \item \textbf{Religious Activities:} Support and promote various faiths.
    \item \textbf{Religious Media and Broadcasting:} Support organizations of all faiths that produce and distribute religious programming, literature, and other communications.
    \item \textbf{Non-Medical Science \& Technology Research:} Support research and services in a variety of scientific disciplines, advancing knowledge and understanding of areas such as energy efficiency, environmental and trade policies, and agricultural sustainability.
    \item \textbf{Social and Public Policy Research:} Support economic and social issues impacting our country today, educate the public, and influence policy regarding healthcare, employment rights, taxation, and other civic ventures.
\end{itemize}


% \begin{table}[h!]
% \centering
% \caption{Full List of Survey Options}
% \label{tab:optionsList}
% \begin{tabular}{p{3.4cm} p{12cm}}
% \toprule
% \textbf{Category} & \textbf{Description} \\
% \midrule
% Animal Rights, Welfare, and Services & Protect animals from cruelty, exploitation, and other abuses, provide veterinary services, and train guide dogs. \\
% Wildlife Conservation & Protect wildlife habitats, including fish, wildlife, and bird refuges and sanctuaries. \\
% Zoos and Aquariums & Support and invest in zoos, aquariums, and zoological societies in communities throughout the country. \\
% Libraries, Historical Societies, and Landmark Preservation & Support public and specialized libraries, historical societies, preservation programs, and historical estates. \\
% Museums & Support and invest in maintaining collections and providing training to practitioners in traditional arts, science, technology, and natural history. \\
% Performing Arts & Support symphonies, orchestras, ballets, operas, theater groups, arts festivals, and cultural centers. \\
% Public Broadcasting and Media & Support public television and radio stations and networks, as well as independent media and communications services. \\
% Community Foundations & Promote giving by managing donor-advised charitable funds and distributing them to community-based charities over time. \\
% Housing and Neighborhood Development & Lead and finance projects to improve communities by providing utility assistance, small business support, and revitalization projects. \\
% Jewish Federations & Support Jewish-oriented programs, organizations, and activities through grantmaking efforts. \\
% United Ways & Identify and resolve community issues through partnerships with schools, government agencies, businesses, and others. \\
% Adult Education Programs and Services & Provide opportunities for adults to expand their knowledge, learn English as a second language, or complete their high school education. \\
% Early Childhood Programs and Services & Provide foundation-level learning and literacy for children before formal schooling. \\
% Education Policy and Reform & Promote research, policy, and reform of educational institutions and systems. \\
% Scholarship and Financial Support & Support students to obtain financial assistance for educational and living expenses. \\
% Special Education & Provide services for gifted children and youth or those with disabilities requiring modified curricula or teaching methods. \\
% Youth Education Programs and Services & Provide programming for school-aged students in disciplines such as art, STEM, and outward-bound learning. \\
% Botanical Gardens, Parks, and Nature Centers & Promote preservation of the environment and lead environmental beautification campaigns. \\
% Environmental Protection and Conservation & Develop strategies to combat pollution, promote conservation, and manage resources sustainably. \\
% Diseases, Disorders, and Disciplines & Seek cures for diseases and disorders and promote specific medical disciplines. \\
% Medical Research & Research causes and cures of diseases and develop new treatments. \\
% Patient and Family Support & Support programs for family members and patients diagnosed with serious illnesses. \\
% Treatment and Prevention Services & Provide medical services and educate the public on disease prevention and health risks. \\
% Advocacy and Education & Support social justice through legal advocacy, social action, and reform measures. \\
% Development and Relief Services & Provide medical care, human services, and economic, educational, and agricultural development services. \\
% Humanitarian Relief Supplies & Distribute donated medical, food, agricultural, and other supplies to those in need. \\
% International Peace, Security, and Affairs & Promote peace, security, cultural exchanges, and improve international relations. \\
% Religious Activities & Support and promote various faiths. \\
% Religious Media and Broadcasting & Support organizations producing religious programming and literature. \\
% Non-Medical Science \& Technology Research & Support research in scientific disciplines, advancing knowledge in areas like energy efficiency and sustainability. \\
% Social and Public Policy Research & Support research on economic and social issues impacting healthcare, employment, taxation, and civic policies. \\
% \bottomrule
% \end{tabular}
% \end{table}
    