\documentclass[sigconf]{acmart}
\settopmatter{authorsperrow=2} % not sure if this is allowed but this looks much better

\usepackage{enumitem}
\usepackage{graphicx}  % another package that works for figures
\usepackage{booktabs} % For formal tables
\usepackage{cleveref} % for better references
\usepackage{caption,subcaption}
% \usepackage[english]{babel}% already included
\usepackage{csquotes}% Recommended
\usepackage{siunitx}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{rotating}
\usepackage{lscape}
\usepackage{afterpage}
\usepackage{hyperref}
\hypersetup{breaklinks=true}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{multirow}
\usepackage[utf8]{inputenc} % Allow Unicode characters

\usepackage{framed} % replacing \usepackage{mdframed}
\usepackage{fontawesome} % for the icon

\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Bibliography
\bibliographystyle{ACM-Reference-Format}
\usepackage{url}

\definecolor{lightgray}{gray}{0.9}
\definecolor{darkgray}{gray}{0.4}
\definecolor{darkred}{rgb}{0.6, 0, 0}

% quote macros
\input{content/macros/quotes}

%% author color
%% color: http://latexcolor.com/
\definecolor{lapislazuli}{rgb}{0.15, 0.38, 0.61}
\newcommand{\hs}[1]{{\color{red}{HS: #1}}}
\newcommand{\tc}[1]{{\color{green}{TC: #1}}}
\newcommand{\lwt}[1]{{\color{olive}{LWT: #1}}}
\newcommand{\kk}[1]{{\color{violet}{KK: #1}}}
\newcommand{\vk}[1]{{\color{blue}{VK: #1}}}
\newcommand{\yhc}[1]{{\color{orange}{YHC: #1}}}
\newcommand{\change}[1]{{\color{black}{#1}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\copyrightyear{2025}
\acmYear{2025}
\setcopyright{cc}
\setcctype{by-nc}
\acmConference[CI 2025]{Collective Intelligence Conference}{August 4--6, 2025}{San Diego, CA, USA}
\acmBooktitle{Collective Intelligence Conference (CI 2025), August 4--6, 2025, San Diego, CA, USA}
\acmDOI{10.1145/3715928.3737474}
\acmISBN{979-8-4007-1489-4/2025/08}


\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
% \title[QV vs Likert]{``\textellipsis I can show what I really like.'': 
% Comparing Quadratic Voting with Likert Surveys at aligning respondents' preferences}

\title[Empirical Exploration of Quadratic Survey Mechanisms]{Budget, Cost, or Both? An Empirical Exploration of Mechanisms in Quadratic Surveys}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.


%% Author list
\input{metadata/authors/tcheng.tex}
\input{metadata/authors/wenting.tex}
\input{metadata/authors/kkarahal.tex}
\input{metadata/authors/hs1.tex}

% %%
% %% By default, the full list of authors will be used in the page
% %% headers. Often, this list is too long, and will overlap
% %% other information printed in the page headers. This command allows
% %% the author to define a more concise list
% %% of authors' names for this purpose.
\renewcommand{\shortauthors}{Ti-Chung Cheng et al.}

\begin{abstract}
    The Quadratic Survey (QS) is an emerging preference elicitation method designed for collective intelligence contexts, where effective decision-making depends on capturing rich individual preferences, including both what people support and how strongly they care. QS sets itself apart from traditional tools through two core mechanisms: a fixed credit budget and a quadratic cost function. This study empirically examines the role of the two components in QS's effectiveness in isolation, by comparing the performance of QS and the Likert scale survey to two variants of QS: Unlimited QS, which removes the budget constraint, and Linear Survey, which replaces the quadratic cost with a linear function. In a controlled experiment with MTurk participants, survey responses from Unlimited QS and Linear Survey were evaluated alongside the existing QS and Likert scale responses reported in prior work, and all responses were compared against an incentive-compatible donation task. Hierarchical Bayesian analyses reveal that QS more effectively aligns expressed preferences with individuals' donation behavior, while omitting either component degrades performance. The results also confirm that both pairwise rankings and interval intensity differences between options captured by QS closely reflect individual behavior, outperforming both the Likert scale and Constant Sum-like surveys. These findings advance our understanding of QS and provide practitioners with an alternative tool to collect reflective individual preferences for collective decision-making contexts such as democratic engagement or public resource allocation.
\end{abstract}

\input{metadata/keywords.tex}

%% Main Text
\maketitle
\input{content/0_Introduction.tex}
\input{content/1_related_works.tex}
\input{content/2_experiment.tex}
\input{content/3_models.tex}
\input{content/4_results.tex}
\input{content/5_discussion.tex}
\input{content/6_conclusion.tex}
\input{content/98_acks.tex}


% \printbibliography
\bibliography{tcheng, references}

% TC:ignore
% \input{content/99_appendix}
% TC:endignore

\end{document}
\endinput

